---
title: "Daily challenges"
author: "Jan-Philipp Kolb"
date: "13 10 2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=F,warning = F,message=F)
```

## Points

```{r}
library(maps)
data(world.cities)
map()
map.cities(world.cities,col=rgb(0,1,0,.05),cex=2,pch=20)
```


## Lines

- get the [bounding box](https://www.rdocumentation.org/packages/osmdata/versions/0.1.6/topics/getbb)


```{r osmdatawb,cache=T}
library(osmdata)
library(osmplotr)
bbox <- getbb("Wiesbaden")
dat_pa <- extract_osm_objects(key = 'highway',
                              value = "primary",
                              bbox = bbox)
dat_sa <- extract_osm_objects(key = 'highway',
                              value = "secondary",
                              bbox = bbox)

map <- osm_basemap(bbox = bbox, bg = c("#F5F5DC"))
map <- add_osm_objects(map, dat_pa, col = c("#00008B"))
map <- add_osm_objects(map, dat_sa, col = "green")
# further objects can be added
print_osm_map(map)

```



## Polygons

- PLZ Shapefiles

```{r}
library(maptools)
data("wrld_simpl")
plot(wrld_simpl,col="red")
```


## Data Challenge 1: OpenStreetMap

- get the [osm data](https://learnosm.org/en/osm-data/getting-data/) 


## Red

```{r mysdata,cache=T,eval=F}
MYS3 <- raster::getData('GADM', country='MYS', level=3)
tmap::qtm(UGA3,"NAME_2")
```



## Green

```{r}
library(tmap)

data(World)
World$fantasy_val <- runif(nrow(World))
qtm(World,"fantasy_val", fill.palette = rgb(0,seq(0,1,.1),0))
```



## Blue

```{r}
library(tmap)
data(World)
World$fantasy_val <- runif(nrow(World))
qtm(World,"fantasy_val", fill.palette = rgb(seq(0,1,.1),0,0))

```


## 9 Monochrome

```{r wormsdat,cache=T,eval=F}
library(osmdata)

bbox <- getbb ("Worms")
dat_osm <- extract_osm_objects (value="highway", bbox = bbox)
qtm(dat_osm,fill=c("#B0B0B0"),borders=c("#8B7D6B"))

```



## 10 Raster

```{r}

path <- "C:/Users/X230/Downloads/NE1_50M_SR_W/NE1_50M_SR_W/"

dat <- raster::stack(paste0(path,"NE1_50M_SR_W.tif"))


sp::spplot(dat,"NE1_50M_SR_W.1")

```


## 11 3D

```{r isosurf,cache=T}
library(plot3D)
x <- y <- runif(100)
z <- rnorm(100)
M <- mesh(x, y, z)
R <- with (M, sqrt(x^2 + y^2 +z^2))
p <- sin(2*R)/(R+1e-3)
isosurf3D(x, y, z, colvar = p, level = 0)
```



## 12 Population

```{r}
library(tmap)
data("World")
qtm(World, fill="pop_est",fill.title="population")
```



## 13 Data Challenge 2: Natural Earth

## 14 Map with a new tool

## 15 Map made without a computer

## 16 Urban/rural

## 17 Land

## 18 Water

```{r watersaarland,cache=T,eval=F}
library(osmplotr)
gc <- geocode_OSM("Berlin")
bbox <- get_bbox (gc$bbox)
dat_osm <- extract_osm_objects (key="natural",
                                value="water", bbox = bbox)
```



## 19 Islands

```{r vutdat,cache=T}
VUT2 <- raster::getData('GADM', country='VUT', level=2)
  qtm(VUT2,fill="green")
```


## 20 Movement

```{r barcelonadat,cache=T,eval=F}

library(osmplotr)
library(ggplot2)
gc <- geocode_OSM("Barcelona")
bbox <- get_bbox (gc$bbox)
dat_osm <- extract_osm_objects (key="route",value="subway", bbox = bbox)
ggplot() + geom_sf(data = dat_osm,aes(col=ref))

```


## 21 Elevation

```{r elavat,cache=T}
library(elevatr)

elevation <- get_elev_raster(dat_pa, z = 9)
plot(elevation)
```



## 22 Boundaries

```{r}
library(maptools)
data("wrld_simpl")
plot(wrld_simpl,col="red")
```



## 23 Data Challenge 3: GHSL

## 24 Historical map

```{r}

c1880 <- rgdal::readOGR("C:/Users/X230/Downloads/1880/cntry1880.shp")
  
tmap::qtm(c1880,fill="royalblue",borders = "lightgray")


# #30daymapchallenge day 17 - historical map - borders of 1880. Historical country GIS data from Thinkquest. Made with tmap #rstats #rspatial package. 

  
# data from:
# http://web.archive.org/web/20080328104539/
# http://library.thinkquest.org:80/C006628/download.html


```



## 25 Interactive map

## 26 Choropleth map

## 27 Heatmap

## The Earth is not flat

```{r}
library(globe)

globeearth()
globeearth(eye=place("everest"),col="royalblue")

```



## 29 NULL

## 30 Metamapping day

